Volunteers in the Clouds: A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2015-12-14 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Split section V
Closes #66

@@

\subsection{$F_{15}:\frac{D}{m}$-group Shifted and $m$-rotated Rastrigin's Function}
JavaScript has been traditionally implemented as an interpreted
language not designed for the development of high performance
systems. On the other hand, current JavaScript  
virtual machines (VMs) are closing the gap, for instance the Google V8 
is an engine specifically designed for the fast execution of 
large JavaScript applications. In order to increase performance
V8 compiles JavaScript source code directly into machine code when it is first executed. 
There are no intermediate byte codes or an interpreter \cite{Gray:2009:GCM:1610564.1610565}.
JavaScript has gained popularity in server-side development using runtime
environments such as Node.js and is also used in desktop and mobile applications. 
%Mario: Creo que el párrafo de arriba sale sobrando
% (Paloma) Agree, I mean, it adds information but in case you have space problems... is ok if you start the section without it
To further evaluate how a current JavaScript implementation could be used by a
computer scientist to develop complex optimization problems,
a benchmark function, which was provided by the CEC2010 Special Session on
Large-Scale Global Optimization \cite{tang2007benchmark} is used in this section. 
The function is described next.

>>>>

\subsection{Experimental trials}
\label{sec:w2Exp}

@@

JavaScript has been traditionally implemented as an interpreted
language not designed for the development of high performance
systems. On the other hand, current JavaScript  
virtual machines (VMs) are closing the gap, for instance the Google V8 
is an engine specifically designed for the fast execution of 
large JavaScript applications. In order to increase performance
V8 compiles JavaScript source code directly into machine code when it is first executed. 
There are no intermediate byte codes or an interpreter \cite{Gray:2009:GCM:1610564.1610565}.
JavaScript has gained popularity in server-side development using runtime
environments such as Node.js and is also used in desktop and mobile applications. 
%Mario: Creo que el párrafo de arriba sale sobrando
% (Paloma) Agree, I mean, it adds information but in case you have space problems... is ok if you start the section without it
To further evaluate how a current JavaScript implementation could be used by a
computer scientist to develop complex optimization problems,
a benchmark function, which was provided by the CEC2010 Special Session on
Large-Scale Global Optimization \cite{tang2007benchmark} is used in this section. 
The function is described next.
